---
title: "VaccineNorway"
author: "Ruiyun Li"
date: "27/04/2021"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

This is a R Markdown document attached to **Prioritizing vaccination by age and social activity to advance societal health benefits in Norway**. authors: Ruiyun Li, Ottar N Bjornstad, Ørjan Olsvik, Nils Chr. Stenseth

In this document, we will use a RAS model that integrates realistic age-structure of both demography and social mixing and plausible coverage, timing and efficacy of vaccine. We evaluate the gains achievable by adopting the The Norwegian Institute of Public Health (FHI) vaccination strategies and its relative effectiveness to various strategies.

## Preparation

We will first prepare the datasets, including

* age pyramid
* age-specific # of contacts
* mobility variation

We include 17 5-year age groups (i.e. 0-4, 5-9, …, 75-79, >80 years old). To illustrate we use Norway as example. Extention to Norwegian cities: using the cities demography.

```{r message = FALSE, warning = FALSE}
require("fields")
wd <- getwd()
Cont_path <- file.path(wd, "Data", "Contact_matrices")
Demo_path <- file.path(wd,"Data","Demography")
Mb_path <- file.path(wd,"Data","Mobility")

# read contact matrix, marginal contacts, demography, mobility
W_NO <- read.csv(paste0(Cont_path,"/", "Contacts_NORWAY.csv"), header = TRUE)[,2:18]
Cmarg_NO <- read.csv(paste0(Cont_path,"/", "margContacts_NORWAY.csv"), header = TRUE)[,2]
Page_NO <- read.csv(paste0(Demo_path, "/", "Pop_NORWAY.csv"), header = TRUE)[,2]
Mb_NO <- read.csv(paste0(Mb_path, "/", "Mb_NO.csv"))[,2]

```

## Model Framework

The model involves coverage, timing and efficacy of vaccine. We define:

* S - Susceptble
* E - Exposed
* Is - Symptomatically infected
* Ia - Aymptomatically infected
* R  - Recovered
* K - Flux into E

- $Q$ - rate of vaccination devided into 5 stages:
- $Q1$ - FHI strategy for HCWs plus 75+ (stage 1)
- $Q2$ - FHI strategy for 20-74 with high risk (stage 2)
- $Q3$ - FHI strategy for 20-74 with other disease (stage 3)
- $Q4$ - FHI/socibility-descending strategy for group X (stage 4)
- $Q5$ - Age/Sociability/Switched strategy for annual vaccination campagin (stage 5)
- $P$ - duration of vaccination
- $q$ - vaccine efficacy (assmued 0.8)
- *R0* - Reproduction number
- 1/$\sigma$ - Average duration of incubation
- 1/$\gamma$ - Average duration of infection
- $\omega$ - Rate of loss of infection
- $\beta0$ - Baseline rate of transmission
- $\beta1$ - Strength of seasonal forcing (assumed 0.1)
- $\phi$ - Force of infection (FOI)
- $\rho1$ - Infectiousness of asymptomatic infections (assumed 0.5)
- $\rho2$ - Proportion of asymptomatic infections
- *C* - Normalized contact matrix
- n   - Number of age groups

```{r}
seirsvages4vacs = function(t,x,params){
  n=17
  S<-x[1:n]
  E<-x[(n+1):(2*n)]
  Is<-x[(2*n+1):(3*n)]
  Ia<-x[(3*n+1):(4*n)]
  R<-x[(4*n+1):(5*n)]
  K<-x[(5*n+1):(6*n)]
  
  with(as.list(params),{
    W = as.matrix(Cnorm)
    # 1 March 2020 - 30 Apr 2021
    if(t<T_ld+Dt_ld){
      W = as.matrix(Cnorm)*scaling[t]
    }
    # 1 May -30 June 2021
    if(t>T_ld2 & t<T_ld2+Dt_ld2){ 
      W = as.matrix(Cnorm)
      epsilon = epsilon2
    }
    WI = W%*%(Is + rho1*Ia)
    beta0 = R0*((sigma+mu)/sigma)*(gamma+mu)
    beta = ifelse(t>306, beta0 * (1+beta1 * cos(2 * pi * (t-306)/365)), beta0)
    phi = k*log(1+beta *WI/(k*N)) # NB() of phi
     
    Q1 <- ifelse(t<T1 | t>T1+Dt1,0,(-log(1-P1)/Dt1))
    Q2 <- ifelse(t<T2 | t>T2+Dt2,0,(-log(1-P2)/Dt2))
    Q3 <- ifelse(t<T3 | t>T3+Dt3,0,(-log(1-P3)/Dt3))
    Q4 <- ifelse(t<T4 | t>T4+Dt4,0,(-log(1-P4)/Dt4))
    Q5 <- if(t>306 & t<Tvacend){
      ifelse((t-306)%%repeat_Interval<(T5-306) | (t-306)%%repeat_Interval>(T5-306)+Dt5,
             0,(-log(1-P5)/Dt5))
    }else{
      0
    }
    
    dS = c(nu,rep(0,n-1))*N + omega*R -phi*S - q*(Q1+Q2+Q3+Q4+Q5)*S - mu*S
    dE = phi*S - sigma*E - mu*E
    dIs = rho2*sigma*E - gamma*Is - mu*Is + epsilon
    dIa = (1-rho2)*sigma*E - gamma*Ia - mu*Ia + epsilon
    dR = gamma*(Is+Ia) + q*(Q1+Q2+Q3+Q4+Q5)*S - omega*R - mu*R
    dK = sigma*E + epsilon

    res<-c(dS,dE,dIs,dIa,dR,dK)
    list(res)
  })
}

```

We define vac2next() which specifcies the prioritized groups. Following FHI vaccination schedule, we firstly prioritize the HWCs, 75+ and people at high risk or have underlying diseases. We then allocate vaccines by two strategies:

* The current FHI age-descending protocol
* The sociability-descending strategies

Further, we assume an annual vaccination campaign with prioritization to the elderly (75+ yr) and three strategies for the rest of the population:

* The age-focused strategy
* The sociability-focused strategy
* The switched strategy: switching from the high-risk older age groups to core-sociable ones

```{r}
vac2next = function(P_age, tot_cov, cov, next2)
{
  # stages 1-3
  age1 = 4:15; t1 = 8; dur1 = 173; cov1 = cov[1]   # HCWs 15-74
  age2 = 16:17; t2 = -5; dur2 = 132; cov2 = cov[2] # 75+
  age3 = 5:15; t3 = 72; dur3 = 109; cov3 = cov[3]  # 20-74 with high risk
  age4 = 12:13; t4 = 98; dur4 = 46; cov4 = cov[4]  # 55-64 with underlying diseases
  age5 = 10:11; t5 = 98; dur5 = 53; cov5 = cov[5]  # 45-54 with underlying diseases
  age6 = 5:9; t6 = 106; dur6 = 52; cov6 = cov[6]   # 20-44 with underlying diseases
  
  ## for the ongoing FHI vaccination (stage 4)
  # The current FHI age-descending protocol
  age7 = 14:15 # 65-74
  age8 = 12:13 # 55-64
  age9 = 10:11 # 45-54
  age10 = 5:9  # 20-44
  
  t7 = t3; dur7 = dur3; cov7 = cov[7]
  t8 = t4; dur8 = dur4; cov8 = cov[8]
  t9 = t5; dur9 = dur5; cov9 = cov[9]
  t10 = t6; dur10 = dur6; cov10 = cov[10]
  
  # The sociability-descending strategies
  soc1 = 3:4    # 10-14, 15-19
  soc2 = c(2,8) # 5-9,35-39
  soc3 = c(9,7) # 40-44, 20-25
  soc4 = c(5,10,6,11,12)
  
  cov11 = ifelse(cov[7]*sum(P_age[age7])>sum(P_age[soc1]), 
                 .99, cov[7]*sum(P_age[age7])/sum(P_age[soc1]))
  cov12 = ifelse(cov[8]*sum(P_age[age8])>sum(P_age[soc2]), 
                 .99, cov[8]*sum(P_age[age8])/sum(P_age[soc2]))
  cov13 = ifelse(cov[9]*sum(P_age[age9])>sum(P_age[soc3]), 
                 .99, cov[9]*sum(P_age[age9])/sum(P_age[soc3]))
  cov14 = ifelse(cov[10]*sum(P_age[age10])>sum(P_age[soc4]), 
                 .99, cov[10]*sum(P_age[age10])/sum(P_age[soc4]))
  
  # Across strategies, vaccination for the prioritized groups in stage 1-3
    P1 = rev(c(rep(cov2,2),rep(cov1,12), rep(0,3)))
    T1 = rev(c(rep(t2,2),rep(t1,12), rep(366,3)))
    Dt1 = rev(c(rep(dur2,2),rep(dur1,12), rep(0,3)))
    
    P2 = c(rep(0,4),rep(cov3,11), rep(0,2))
    T2 = c(rep(366,4),rep(t3,11), rep(366,2))
    Dt2 = c(rep(0,4),rep(dur3,11), rep(0,2))
    
    P3 = rev(c(rep(0,4),rep(cov4,2),rep(cov5,2),rep(cov6,5), rep(0,4)))
    T3 = rev(c(rep(366,4),rep(t4,2),rep(t5,2),rep(t6,5), rep(366,4)))
    Dt3 = rev(c(rep(0,4),rep(dur4,2),rep(dur5,2),rep(dur6,5), rep(0,4)))
  
  # Baseline scenario: no vaccination in stage 4-5
  if(next2 == "base"){
    
    P4 = c(rep(0,17)); T4 = c(rep(366,17)); Dt4 = c(rep(0,17))
    P5 = c(rep(0,17)); T5 = c(rep(366,17)); Dt5 = c(rep(0,17))
    
  }
  
  # The current FHI age-descending protocol
  if(next2 == "next2younger"){
    
    P4 = rev(c(rep(0,2),rep(cov7,2),rep(cov8,2),rep(cov9,2),rep(cov10,5),rep(0,4))) 
    T4 = rev(c(rep(366,2),rep(t7,2),rep(t8,2),rep(t9,2),rep(t10,5),rep(366,4)))
    Dt4 = rev(c(rep(0,2),rep(dur7,2),rep(dur8,2),rep(dur9,2),rep(dur10,5),rep(0,4)))
    
    P5 = c(rep(0,17)); T5 = c(rep(366,17)); Dt5 = c(rep(0,17))
    
  }
  
  # The sociability-descending strategies
  if(next2 == "next2social"){
    
    P4 = rev(c(rep(0,5),rep(cov14,3),cov13,cov12,cov13,rep(cov14,2),rep(cov11,2),cov12,0)) 
    T4 = rev(c(rep(366,5),rep(t10,3),t9,t8,t9,rep(t10,2),rep(t7,2),t8,366))
    Dt4 = rev(c(rep(0,5),rep(dur10,3),dur9,dur8,dur9,rep(dur10,2),rep(dur7,2),dur8,0))
    
    P5 = c(rep(0,17)); T5 = c(rep(366,17)); Dt5 = c(rep(0,17))
    
  }
  
  ## for annual vaccination (stage 5)
  # The age-focused strategy
  if(next2 == "ann.age"){
 
    P4 = rev(c(rep(0,2),rep(cov7,2),rep(cov8,2),rep(cov9,2),rep(cov10,5),rep(0,4))) 
    T4 = rev(c(rep(366,2),rep(t7,2),rep(t8,2),rep(t9,2),rep(t10,5),rep(366,4)))
    Dt4 = rev(c(rep(0,2),rep(dur7,2),rep(dur8,2),rep(dur9,2),rep(dur10,5),rep(0,4)))
    
    P5 = T5 = Dt5 = rep(0, 17)
    elderly = 16:17; senior = 10:15; others = 1:9
    P5[elderly] = .99; Dt5[elderly] = 92/3; T5[elderly] = 273
    P5[senior] = .99; Dt5[senior] = 92/3; T5[senior] = 273+92/3
    P5[others] = (tot_cov-sum(P_age[c(elderly,senior)]))/sum(P_age[others])
    Dt5[others] = 92/3; T5[others] = 273+92/3*2
    
  }
  
  # The sociability-focused strategy
  if(next2 == "ann.soc"){

    P4 = rev(c(rep(0,2),rep(cov7,2),rep(cov8,2),rep(cov9,2),rep(cov10,5),rep(0,4)))
    T4 = rev(c(rep(366,2),rep(t7,2),rep(t8,2),rep(t9,2),rep(t10,5),rep(366,4)))
    Dt4 = rev(c(rep(0,2),rep(dur7,2),rep(dur8,2),rep(dur9,2),rep(dur10,5),rep(0,4)))

    P5 = T5 = Dt5 = rep(0, 17)
    elderly = 16:17; coresoc = c(3,4,2,8,9,7); others = c(5,10,6,11,12,1,13,14,15)
    P5[elderly] = .99; Dt5[elderly] = 92/3; T5[elderly] = 273
    P5[coresoc] = .99; Dt5[coresoc] = 92/3; T5[coresoc] = 273+92/3
    P5[others] = (tot_cov-sum(P_age[c(elderly, coresoc)]))/sum(P_age[others]) 
    Dt5[others] = 92/3; T5[others] = 273+92/3
    
  }

  # The switched strategy
  if(next2 == "ann.switch"){

    P4 = rev(c(rep(0,2),rep(cov7,2),rep(cov8,2),rep(cov9,2),rep(cov10,5),rep(0,4))) 
    T4 = rev(c(rep(366,2),rep(t7,2),rep(t8,2),rep(t9,2),rep(t10,5),rep(366,4)))
    Dt4 = rev(c(rep(0,2),rep(dur7,2),rep(dur8,2),rep(dur9,2),rep(dur10,5),rep(0,4)))
    
    P5 = T5 = Dt5 = rep(0, 17)
    elderly = 16:17; senior = 10:15; coresoc = c(3,4,2,8,9,7); others = c(6,5,1)
    rest1 = rest2 = 0
    P5[elderly] = .99; Dt5[elderly] = 92/3; T5[elderly] = 273
    if(sum(P_age[senior])<.5*(tot_cov-sum(P_age[elderly]))){
      P5[senior] = .99; T5[senior] = 273+92/3; Dt5[senior] = 92/3
      rest1 = .5*(tot_cov-sum(P_age[elderly])) - sum(P_age[senior]*.99)
    }else{
      P5[senior] = .5*(tot_cov-sum(P_age[elderly]))/sum(P_age[senior]); 
      T5[senior] = 273+92/3; Dt5[senior] = 92/3
    }
    if(sum(P_age[coresoc])<.5*(tot_cov-sum(P_age[elderly]))){
      P5[coresoc] = .99; T5[coresoc] = 273+92/3*2; Dt5[coresoc] = 92/3
      rest2 = .5*(tot_cov-sum(P_age[elderly])) - sum(P_age[coresoc]*.99)
    }else{
      P5[coresoc] = .5*(tot_cov-sum(P_age[elderly]))/sum(P_age[coresoc]); 
      T5[coresoc] = 273+92/3*2; Dt5[coresoc] = 92/3
    }
    P5[others] = (rest1+rest2)/sum(P_age[others]); 
    T5[others] = 273+92/3*2; Dt5[others] = 92/3
  }
  
  return(list(P1=P1, T1=T1, Dt1=Dt1, P2=P2, T2=T2, Dt2=Dt2,
              P3=P3, T3=T3, Dt3=Dt3, P4=P4, T4=T4, Dt4=Dt4, 
              P5=P5, T5=T5, Dt5=Dt5))
}

```

Model is initialized with 0.1% symptomatically and asymptomatically infected individuals. We define function for simulation:

```{r}
seirsvages4vacssim = function(R0, P_age, W, P1, T1, Dt1, P2, T2, Dt2, P3, T3, Dt3, 
                              P4, T4, Dt4, P5, T5, Dt5, durIm, scaling, 
                              Tvacend, repeat_Interval, rho2, k, Cmarg)
{
  pars = list(N = 1, sigma=1/3, gamma = 1/5, nu = 0, mu = 0, beta1=.1, 
              R0 = R0, Cnorm = W, Cmarg = Cmarg, omega=1/durIm, 
              T_ld = 12, Dt_ld = 306+120-12, scaling = scaling, epsilon = 1e-10,
              T_ld2 = 306+120, Dt_ld2 = 181-120, epsilon2 = 1e-8, 
              rho1=.5, rho2=rho2, k=k,
              q = .8, P1 = P1, Dt1 = Dt1, T1 = 306+T1, # 306: days from 01.03-31.12.20
              P2 = P2, Dt2 = Dt2, T2 = 306+T2,         # T1-T4: days from 01.01.21
              P3 = P3, Dt3 = Dt3, T3 = 306+T3,
              P4 = P4, Dt4 = Dt4, T4 = 306+T4,
              P5 = P5, Dt5 = Dt5, T5 = 306+T5,         # T5: days from 01 Jan/year
              Tvacend=Tvacend, repeat_Interval=repeat_Interval)
  ystart = c(S=.98*P_age,E=0.01*P_age,Is=.01*P_age,Ia=.01*P_age,R=0*P_age,K=0*P_age)
  out = as.data.frame(ode(ystart, times=times, func = seirsvages4vacs, parms = pars))
  
  return(out)
}

sim_vac2next = function(R0, P_age, tot_cov, scaling, cov, next2, 
                        Tvacend, repeat_Interval, k)
{
  out = seirsvages4vacssim(R0=R0, P_age=P_age, W=W_NO,durIm=365, k = k, 
                           scaling = scaling, rho2 = rho2, Cmarg = Cmarg_NO,
                           P1 = vac2next(P_age, tot_cov, cov, next2)$P1,
                           T1 = vac2next(P_age, tot_cov, cov, next2)$T1, 
                           Dt1 = vac2next(P_age, tot_cov, cov, next2)$Dt1,
                           P2 = vac2next(P_age, tot_cov, cov, next2)$P2, 
                           T2 = vac2next(P_age, tot_cov, cov, next2)$T2,
                           Dt2 = vac2next(P_age, tot_cov, cov, next2)$Dt2,
                           P3 = vac2next(P_age, tot_cov, cov, next2)$P3, 
                           T3 = vac2next(P_age, tot_cov, cov, next2)$T3,
                           Dt3 = vac2next(P_age, tot_cov, cov, next2)$Dt3,
                           P4 = vac2next(P_age, tot_cov, cov, next2)$P4, 
                           T4 = vac2next(P_age, tot_cov, cov, next2)$T4,
                           Dt4 = vac2next(P_age, tot_cov, cov, next2)$Dt4,
                           P5 = vac2next(P_age, tot_cov, cov, next2)$P5, 
                           T5 = vac2next(P_age, tot_cov, cov, next2)$T5,
                           Dt5 = vac2next(P_age, tot_cov, cov, next2)$Dt5,
                           Tvacend = Tvacend,repeat_Interval=repeat_Interval)
  
  return(out)
}

```

We now simulate the model:

```{r}
library(deSolve)
n = 17                # 17 age groups
times = 1:(306+365*5) # 01.03.20 - 31.12.25
R0 = 3.5              # FHI report (R0 around 01.03.20)
rho1 = .5
rho2 = c(.29,.29, .21,21, .27,.27, .33,.33, .4,.4, 
         .49,.49, .63,.63, .69,.69,.69)    # ref. Davies et al. Nature Med
cov = c(0.093, 0.992, 0.032, 0.170, 0.132, 
        0.061, 0.818, 0.642, 0.748, 0.861) # FHI coverage for each group
dose1 = sum(Page_NO[5:17]) # total doses covering all adults
dose2 = .9                 # total doses covering 90% of the population

NO_base = sim_vac2next(R0, Page_NO, tot_cov=dose1, scaling=Mb_NO, k=.015, 
                       cov=cov, next2="base",Tvacend=0,repeat_Interval=365*5)
NO_vacage = sim_vac2next(R0, Page_NO, tot_cov=dose1, scaling=Mb_NO, k=.015, 
                         cov=cov, next2="next2younger",0,365*5)
NO_vacsoc = sim_vac2next(R0, Page_NO, tot_cov=dose1, scaling=Mb_NO, k=.015, 
                         cov=cov, next2="next2social",0,365*5)

NO_ann.age_d1 = sim_vac2next(R0, Page_NO, tot_cov=dose1, scaling=Mb_NO, 
                             k=.015, cov=cov, next2="ann.age",365*5,365)
NO_ann.soc_d1 = sim_vac2next(R0, Page_NO, tot_cov=dose1, scaling=Mb_NO, 
                             k=.015, cov=cov, next2="ann.soc",365*5,365)
NO_ann.switch_d1 = sim_vac2next(R0, Page_NO, tot_cov=dose1, scaling=Mb_NO, 
                                k=.015, cov=cov, next2="ann.switch",365*5,365)
NO_ann.age_d2 = sim_vac2next(R0, Page_NO, tot_cov=dose2, scaling=Mb_NO, k=.015, 
                             cov=cov, next2="ann.age",365*5,365)
NO_ann.soc_d2 = sim_vac2next(R0, Page_NO, tot_cov=dose2, scaling=Mb_NO, k=.015, 
                             cov=cov, next2="ann.soc",365*5,365)
NO_ann.switch_d2 = sim_vac2next(R0, Page_NO, tot_cov=dose2, scaling=Mb_NO, k=.015, 
                                cov=cov, next2="ann.switch",365*5,365)

```

To evaluate the effectiveness of vaccination strategies, we estimate the reduction of infections as compared with baseline scenario without vaccination. We define Inf_avert() to evaluate the effectiveness of the FHI age-descending strategy *versus* the sociability-descending strategy. Additionally, we define Inf_avert2() to evaluate the effectiveness of the age-focused and sociability-focused strategies *versus* the switched strategy. 

```{r}
Inf_avert = function(Infs, t1, t2)  # t1: start_vac_next, t2: est_time
{
  Infs0 = apply(Infs[,1:17],1,sum)  # baseline
  Infs1 = apply(Infs[,18:34],1,sum) # vaccinating by age 
  Infs2 = apply(Infs[,35:51],1,sum) # vaccinating by sociability
  
  t1 = 306+t1
  t2 = 306+t2
  Infs_avert1 = (sum(Infs0[t1:t2]) - sum(Infs1[t1:t2])) /sum(Infs0[t1:t2])
  Infs_avert2 = (sum(Infs0[t1:t2]) - sum(Infs2[t1:t2])) /sum(Infs0[t1:t2])
  avert = c(Infs_avert1, Infs_avert2)
  
  return(c(avert))
}

Inf_avert2 = function(Infs, t1, t2) # t1: start_vac_next, t2: est_time
{
  Infs0 = apply(Infs[,1:17],1,sum)  # baseline
  Infs1 = apply(Infs[,18:34],1,sum) # vaccinating by age 
  Infs2 = apply(Infs[,35:51],1,sum) # vaccinating by sociability
  Infs3 = apply(Infs[,52:68],1,sum) # switched vaccination
  
  t1 = 306+t1
  t2 = 306+t2
  Infs_avert1 = (sum(Infs0[t1:t2]) - sum(Infs1[t1:t2])) /sum(Infs0[t1:t2])
  Infs_avert2 = (sum(Infs0[t1:t2]) - sum(Infs2[t1:t2])) /sum(Infs0[t1:t2])
  Infs_avert3 = (sum(Infs0[t1:t2]) - sum(Infs3[t1:t2])) /sum(Infs0[t1:t2])
  avert = c(Infs_avert1, Infs_avert2, Infs_avert3)
  
  return(c(avert))
}

```

The effectiveness of the FHI and scociability strategies are estimated by the reduction of infections by the end of the vaccination and after two months of the end of the vaccination. The effectiveness of the age-focused/sociability-focused/switched strategies are estimated by the reduction of infections over a year.

```{r}
# FHI age-descending strategy vs. the sociability-descending strategy
Inf_NO = cbind(NO_base[,(2*n+2):(3*n+1)]+NO_base[,(3*n+2):(4*n+1)],
               NO_vacage[,(2*n+2):(3*n+1)]+NO_vacage[,(3*n+2):(4*n+1)],
               NO_vacsoc[,(2*n+2):(3*n+1)]+NO_vacsoc[,(3*n+2):(4*n+1)])

start_vac_next = 72 # initial vaccination by age/sociability
end_vac_next = 181  # ending vaccinating all adults

Inf_avert(Inf_NO, start_vac_next, end_vac_next)
Inf_avert(Inf_NO, start_vac_next, end_vac_next+60)

barplot(c(Inf_avert(Inf_NO, start_vac_next, end_vac_next),NA,
          Inf_avert(Inf_NO, start_vac_next, end_vac_next+60),NA),
        ylim=c(0,.4), beside = FALSE, border="white",space=0,
        col=rep(c("#f1b14d","darkcyan",NA),2),tck=-.01,
        ylab="Reduction of infections",
        font=2,font.axis=2,font.lab=2,cex.lab=1.3)

# age-focused and sociability-focused strategies vs. the switched strategy
Inf_NO_ann.d1 = cbind(NO_base[,(2*n+2):(3*n+1)]+NO_base[,(3*n+2):(4*n+1)],
                      NO_ann.age_d1[,(2*n+2):(3*n+1)]+NO_ann.age_d1[,(3*n+2):(4*n+1)],
                      NO_ann.soc_d1[,(2*n+2):(3*n+1)]+NO_ann.soc_d1[,(3*n+2):(4*n+1)],
                      NO_ann.switch_d1[,(2*n+2):(3*n+1)]+NO_ann.switch_d1[,(3*n+2):(4*n+1)])

Inf_NO_ann.d2 = cbind(NO_base[,(2*n+2):(3*n+1)]+NO_base[,(3*n+2):(4*n+1)],
                      NO_ann.age_d2[,(2*n+2):(3*n+1)]+NO_ann.age_d2[,(3*n+2):(4*n+1)],
                      NO_ann.soc_d2[,(2*n+2):(3*n+1)]+NO_ann.soc_d2[,(3*n+2):(4*n+1)],
                      NO_ann.switch_d2[,(2*n+2):(3*n+1)]+NO_ann.switch_d2[,(3*n+2):(4*n+1)])

Inf_avert2(Inf_NO_ann.d1, 273, 273+365)
Inf_avert2(Inf_NO_ann.d2, 273, 273+365)

barplot(c(Inf_avert2(Inf_NO_ann.d1, 273, 273+365),NA,
          Inf_avert2(Inf_NO_ann.d2, 273, 273+365),NA),
        ylim=c(0,.4), beside = FALSE, border="white",space=0,
        col=rep(c("#f1b14d","darkcyan","black",NA),2),tck=-.01,
        ylab="Reduction of infections",
        font=2,font.axis=2,font.lab=2,cex.lab=1.3)

```
